### 2023-11-21 main.tex
Update

\paragraph{Organization of the paper}
\section{The stirring process with open boundaries}
\subsection{Informal description of the process}
The process studied in this paper is the {\em multi-species stirring process}
with open boundaries. 
In words, the dynamics is described as follows. Each site
of a connected graph can host up to $\nu\in \mathbb{N}$ particles.
The particles have a {\em type} (sometimes called {\em species} or {\em color})
which can take $N$ values.
Then, the dynamics has two parts: on each edge of the graph, 
any two types are swapped at rate $1$; additionally, on each site $x$, 
a particles of a given type (if present) is replaced with a
particle of type $a$ at rate $\alpha_a^x >0$.
The swap dynamics taking place on the edges is of Kawasaki-type 
with $N$ conservation laws
(the total number of particles of each type). 
The site-dynamics is instead of Glauber-type. 
In the long-time limit, a so-called non-equilibrium
steady state sets in.

@@

The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\qquad\qquad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle\dt
	\end{cases}
\end{equation}  
The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
%{\color{red} Is this remark relevant for us?}
%\newline 
%\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
\\ \\
%\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
%\begin{equation}
%   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}\dt
%\end{equation}
%{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
The process with generator \eqref{Generator} can be described in terms of $gl(N)$ Lie algebra generators. The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site. Namely,
a vector $|{\bf n}\rangle \in \Omega$ can be written as
%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
%{\color{blue}
%	\begin{equation*}
%		|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1},\ldots,n_{N}\rangle_{x}\right)
%	\end{equation*}}
%where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have 
with $\sum_{a=1}^{N}n_{a}^{x}=\nu$ for any $x\in V$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}\,.
\end{equation}
We introduce the Hamiltonian operator
\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian that describes the interaction between two connected sites is
\begin{equation}\label{edgeHamiltonian}
\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
\end{equation}
Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
acting trivially as the identity on the other sites). 
Following  \cite{belitsky2015self}, the Hamiltonian and the Markov generator are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}\dt
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf m}\in \Omega}}f( {\bf m})\langle  {\bf m}|
\end{equation}

We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the quadratic Casimir of $gl(N)$
\begin{equation}\label{secondCasimir}
    C=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
that acts diagonally as $C|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
More precisely,  considering the standard coproduct 
\begin{equation}
\begin{split}
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\end{split}
\end{equation}
we have 
\begin{equation}
\Delta(C)=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C\otimes \mathbbm{1}+\mathbbm{1}\otimes C\,.
\end{equation}
Then, one can check that 
\begin{equation}\label{hamiltonianCasimir}
	\mathcal{H}_{x,y}=\frac{1}{2}\Delta_{x,y}(C)-\twoj(2\twoj+N)
\end{equation}
where $\Delta_{x,y}(C)$ denotes a copy of $\Delta(C)$ acting on  the sites of edge $(x,y)\in \mathcal{E}$ and acting trivially on the other sites of the graph.

@@

	H_{\text{bulk}}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}

@@

@@

	\Omega^{'}=\left\{(\tau_{1},\ldots,\tau_{L})\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}

@@

    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\widetilde{\mathcal{L}}D(\eta,\cdot)\right)(\xi)

@@

    \sum_{\eta'\in\,\Omega}\mathcal{L}(\eta,\eta')D(\eta',\xi)=\sum_{\xi'\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi')D(\eta,\xi')

@@

Since \eqref{dualityMatrix} is product over sites, proving \eqref{DualityRelation} is equivalent to showing that 
\begin{equation}\label{edgeDualRealtion}
    \mathcal{H}_{x,y}^{T}D=D\mathcal{H}_{x,y}\qquad \forall (x,y)\in \mathcal{E}
\end{equation}
and 
\begin{equation}\label{siteDualRelation}
    H_{x}^{T}D=D\widetilde{H}_{x}\qquad \forall x\in V.
\end{equation}
We perform the proof of duality in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove the bulk duality \eqref{edgeDualRealtion}; finally we will show the boundary duality \eqref{siteDualRelation}. 
As a preliminary result we note that 
\begin{equation}\label{transpositionPropertyR}
(E_{ba}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
\end{equation}
that follows immediately from the definition of $E_{ab}$. 
\begin{comment}

\begin{align*}
R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
	\\&
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\\&
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
 \\=&\sum_{r^{x}\in \Omega_{x}}
	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
	\\=&
	\left(E_{ba}^{x}\right)^{T}
\end{align*}
where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
\end{comment}
\paragraph{Elements of the duality matrix.}
Consider the matrix $D$ defined in \eqref{dualityMatrix}.
We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
\begin{equation}\label{proofDualityElements}
\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
\end{equation}
Fix an arbitrary site $x\in V$, then we have that 
\begin{align*}
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
\end{align*}
where we used \eqref{transpositionPropertyR}. \\
On one hand, on the extra-site $u(x)$ we have 
\begin{align*}
\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
\end{align*}
where  we used the orthogonality relation \eqref{ortho}. 
On the other hand, on the site $x$, we have 
\begin{align*}
&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
\\&
\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
%\\&=
%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
%\\&
%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}
\\& 
\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
\end{align*}
where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
\begin{flushright}
    $\square$
\end{flushright}

@@

\begin{corollary}[Correlations via duality]

@@

\textbf{Proof}:

@@

\textbf{Proof:}

@@

\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}

@@

+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}

@@

	f(c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}

@@

	g_{j}(x_{j},c_{j},\ldots,c_{m})=\left(L+2-x_{j}-\sum_{k=j}^{m}c_{k}\right)^{c_{j}}

@@

\paragraph{Proof of formula \eqref{ResulsBasis}} 

@@

	\end{pmatrix}%\quad \forall a\in \{1,\ldots,N-1\}\dt

@@

	\end{pmatrix}%=\begin{pmatrix} 

@@

	\end{pmatrix}%\qquad\forall a\in \{1,\ldots,N-1\}\dt

@@

	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\qquad %\forall a\in \{1,\ldots,N-1\}\dt

@@

	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1

@@

	(1+n)!

@@

@@

	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle

>>>>

 \textbf{Some interesting references and extensions?}:
 Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
 Use exact solution to compute large deviation rate function extending to the multi-species case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
 Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
 Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term. Extend the duality to stirring models with different mechanism of transition \cite{chatterjee2023multi}.

\paragraph{Organization of the paper}
%
%
%
%
\section{The stirring process with open boundaries}
\subsection{Informal description of the process}
The process studied in this paper is the {\em multi-species stirring process}
with open boundaries. 
In words, the dynamics is described as follows. Each site
of a connected graph can host up to $\nu\in \mathbb{N}$ particles.
The particles have a {\em type} (sometimes called {\em species} or {\em color})
which can take $N$ values.
Then, the dynamics has two parts: on each edge of the graph, 
any two types are swapped at rate $1$; additionally, on each site $x$, 
a particles of a given type (if present) is replaced with a
particle of type $a$ at rate $\alpha_a^x >0$.
The swap dynamics taking place on the edges is of Kawasaki-type 
with $N$ conservation laws
(the total number of particles of each type). 
The site-dynamics is instead of Glauber-type. 
In the long-time limit, a so-called non-equilibrium
steady state sets in.

@@

The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
\begin{equation}\label{actionE}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\qquad\qquad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle\dt
The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
%{\color{red} Is this remark relevant for us?}
%\newline 
%\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
\\ \\
%\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
%   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}\dt
%{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
The process with generator \eqref{Generator} can be described in terms of $gl(N)$ Lie algebra generators. The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site. Namely,
a vector $|{\bf n}\rangle \in \Omega$ can be written as
%We now define the equivalent of \eqref{stateSpace} in the vector notation
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%where we denote 
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
%	\begin{equation*}
%		|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1},\ldots,n_{N}\rangle_{x}\right)
%	\end{equation*}}
%where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have 
with $\sum_{a=1}^{N}n_{a}^{x}=\nu$ for any $x\in V$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}\,.
We introduce the Hamiltonian operator
\begin{equation}\label{OriginalHamiltonian}
		H=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
where the edge Hamiltonian that describes the interaction between two connected sites is
\begin{equation}\label{edgeHamiltonian}
\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
acting trivially as the identity on the other sites). 
Following  \cite{belitsky2015self}, the Hamiltonian and the Markov generator are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}\dt
The action of the generator can also be expressed as 
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
    \langle f|=\sum_{ {{\bf m}\in \Omega}}f( {\bf m})\langle  {\bf m}|\dt
We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the quadratic Casimir of $gl(N)$
\begin{equation}\label{secondCasimir}
    C=\sum_{a,b=1}^{N}E_{ab}E_{ba}\co
that acts diagonally as $C|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
More precisely,  considering the standard coproduct 
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\Delta(C)=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C\otimes \mathbbm{1}+\mathbbm{1}\otimes C\,.
Then, one can check that 
\begin{equation}\label{hamiltonianCasimir}
	\mathcal{H}_{x,y}=\frac{1}{2}\Delta_{x,y}(C)-\twoj(2\twoj+N)
where $\Delta_{x,y}(C)$ denotes a copy of $\Delta(C)$ acting on  the sites of edge $(x,y)\in \mathcal{E}$ and acting trivially on the other sites of the graph.

@@

	H_{\text{bulk}}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}\dt

@@

	n_{a}^{x}=\delta_{\tau_{x},a}\dt

@@

	\Omega^{'}=\left\{(\tau_{1},\ldots,\tau_{L})\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}\dt

@@

    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\widetilde{\mathcal{L}}D(\eta,\cdot)\right)(\xi)\dt

@@

    \sum_{\eta'\in\,\Omega}\mathcal{L}(\eta,\eta')D(\eta',\xi)=\sum_{\xi'\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi')D(\eta,\xi')\co

@@

Since \eqref{dualityMatrix} is product over sites, proving \eqref{DualityRelation} is equivalent to showing that 
\begin{equation}\label{edgeDualRealtion}
    \mathcal{H}_{x,y}^{T}D=D\mathcal{H}_{x,y}\qquad \forall (x,y)\in \mathcal{E}
\end{equation}
and 
\begin{equation}\label{siteDualRelation}
    H_{x}^{T}D=D\widetilde{H}_{x}\qquad \forall x\in V.
\end{equation}
We perform the proof of duality in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove the bulk duality \eqref{edgeDualRealtion}; finally we will show the boundary duality \eqref{siteDualRelation}. 
As a preliminary result we note that 
\begin{equation}\label{transpositionPropertyR}
(E_{ba}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V\co
\end{equation}
that follows immediately from the definition of $E_{ab}$. 
\begin{comment}

\begin{align*}
R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
	\\&
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\\&
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
 \\=&\sum_{r^{x}\in \Omega_{x}}
	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
	\\=&
	\left(E_{ba}^{x}\right)^{T}
\end{align*}
where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
\end{comment}
\paragraph{Elements of the duality matrix.}
Consider the matrix $D$ defined in \eqref{dualityMatrix}.
We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
\begin{equation}\label{proofDualityElements}
\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
\end{equation}
Fix an arbitrary site $x\in V$, then we have that 
\begin{align}
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
\end{align}
where we used \eqref{transpositionPropertyR}. \\
On one hand, on the extra-site $u(x)$ we have 
\begin{align}
\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
\end{align}
where  we used the orthogonality relation \eqref{ortho}. 
On the other hand, on the site $x$, we have 
\begin{align}
&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)\nonumber
\\&
\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
%\\&=
%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
%\\&
%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}\nonumber
\\& 
\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
\\&=
\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
\end{align}
where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
\begin{flushright}
    $\square$
\end{flushright}

@@

\begin{corollary}[Correlations via duality]\label{Corolollary-ABS_Corr-abstract}

@@

\textbf{Proof of Corollary \ref{Corolollary-ABS_Corr-abstract}}:

@@

\textbf{Proof of \ref{Corollary-NESS-ABS}:}

@@

\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\dt

@@

+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\dt

@@

	f(c_{1},\ldots,c_{m})=\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}

@@

	g_{j}(x_{j},c_{j},\ldots,c_{m})=\left(L+2-x_{j}-\sum_{k=j}^{m}c_{k}\right)^{c_{j}}\dt

@@

\paragraph{Proof of \eqref{ResulsBasis}} 

@@

	\end{pmatrix}\dt%\quad \forall a\in \{1,\ldots,N-1\}\dt

@@

	\end{pmatrix}\dt%=\begin{pmatrix} 

@@

	\end{pmatrix}\dt%\qquad\forall a\in \{1,\ldots,N-1\}\dt

@@

	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\dt %\forall a\in \{1,\ldots,N-1\}\dt

@@

	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle\co W|%\qquad\forall a=1,\ldots,N-1

@@

	(1+n)!\dt

@@

		1\qquad &\text{if}\quad \tau_{x}= N\dt

@@

	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\dt
